Verification of Stencil Computations through Spatial Specifications

### 2016-07-06 paper.tex
Fixing the text in the Stencils categories subsection.

\textbf{All reflexive} The vast majority (X\%) of stencils were
reflexive in every dimension of the array. These most often correspond
to applying point-wise transformations to data such as scaling
e.g. \begin{minted}{fortran}
ZZ1(I,K) = .000041868*ZZ1(I,K)
\end{minted}

\textbf{All-reflexive} stencils are reflexive in every dimension of the array. These most often correspond to applying point-wise transformations to data such as scaling e.g. \mintinline{fortran}{ZZ1(I,K) = .000041868*ZZ1(I,K)}. Arrays with this class of stencil must be indexed by all the induction variables used in the LHS without any offsets.

\textbf{Some-reflexive} stencils consist of only reflexive terms but leave some dimensions unspecified. Examples in this class include \mintinline{fortran}{leafpools(:,age_class)=leafpool(:,1)} (which contains an implicit loop), and \mintinline{fortran}{RVM(J,I2) = VRFO(ivar,J)} where \mintinline{fortran}{J} is the induction variable. Arrays with this class of stencil can be indexed by a subset of the LHS induction variables but again without any offsets.

\textbf{Single-action} stencils consist of a single \term{backward},\term{forward}, or \term{centered} term and some number of reflexive terms.
% /home/mrd45/src/corpus/geos-chem/GTMM/CasaRegridModule.F90:645
\begin{minted}{fortran}
do j=2,jm-ig
   do i=1,im
      != stencil readOnce, (backward(depth=1, dim=2))*(reflexive(dim=1)) :: dm, q
      al(i,j) = 0.5e+0_fp*(q(i,j-1)+q(i,j)) + r3*(dm(i,j-1) - dm(i,j))
   enddo
enddo
\end{minted}

\textbf{Single-action-irreflexive} stencils consist of a single \term{backward},\term{forward}, or \term{centered} irreflexive term and some number of reflexive terms.
% /home/mrd45/src/corpus/geos-chem/GeosRad/rrtmg_lw_rtrnmc.F90:355
\begin{minted}{fortran}
do lev = nlayers, 1, -1
    ! ...
    radld = radld - radld * (atrans(lev) + &
       efclfrac(lev,igc) * (1. - atrans(lev))) + &
       gassrc + cldfmc(igc,lev) * &
       (bbdtot * atot(lev) - gassrc)
    != stencil readOnce, (forward(depth=1, dim=2, irreflexive)) :: cldfmc
    drad(lev-1) = drad(lev-1) + radld
\end{minted}
Notice in this example how the read from \mintinline{fortran}{cldfmc} flows through onto the line with the stencil.

>>>>

\textbf{All-reflexive} The vast majority (X\%) of stencils were
reflexive in every dimension of the array. These most often correspond
to applying point-wise transformations to data such as scaling
e.g. \begin{minted}{fortran}
ZZ1(I,K) = .000041868*ZZ1(I,K)
\end{minted}
Arrays with this class of stencil must be indexed by all the induction
variables used in the LHS without any offsets.

\textbf{Some-reflexive} stencils consist of only reflexive terms but
leave some dimensions unspecified. Two examples in this class are listed:
\begin{minted}{fortran}
leafpools(:,age_class)=leafpool(:,1)
RVM(J,I2) = VRFO(ivar,J)
\end{minted}
where for the first example \mintinline{fortran}{leafpools} contains an
implicit loop, and for the second example \mintinline{fortran}{J} is
the induction variable. Arrays with this class of stencil can be
indexed by a subset of the LHS induction variables but again without
any offsets.

\textbf{Single-action} stencils consist of a single \term{backward},
\term{forward}, or \term{centered} term and some number of reflexive
terms.
% /home/mrd45/src/corpus/geos-chem/GTMM/CasaRegridModule.F90:645
\begin{minted}{fortran}
do j=2,jm-ig
   do i=1,im
      != stencil readOnce, (backward(depth=1, dim=2))*(reflexive(dim=1)) :: dm, q
      al(i,j) = 0.5e+0_fp*(q(i,j-1)+q(i,j)) + r3*(dm(i,j-1) - dm(i,j))
   enddo
enddo
\end{minted}

\textbf{Single-action-irreflexive} stencils consist of a single
\term{backward}, \term{forward}, or \term{centered} irreflexive term
and some number of reflexive terms.
% /home/mrd45/src/corpus/geos-chem/GeosRad/rrtmg_lw_rtrnmc.F90:355
\begin{minted}{fortran}
do lev = nlayers, 1, -1
    ! ...
    radld = radld - radld * (atrans(lev) + &
       efclfrac(lev,igc) * (1. - atrans(lev))) + &
       gassrc + cldfmc(igc,lev) * &
       (bbdtot * atot(lev) - gassrc)
    != stencil readOnce, (forward(depth=1, dim=2, irreflexive)) :: cldfmc
    drad(lev-1) = drad(lev-1) + radld
\end{minted}
Notice that, in this last example, the read from
\mintinline{fortran}{cldfmc} flows through onto the line with the
stencil.
